### 2022-07-24 latex/Chapters/Examples.tex
update

\afblue
\paragraph{}{\textbf{python code -- deep reinforcement learner}}
\begin{python}
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deepreinforcementlearner import DeepReinforcementLearner
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n = 4
    m = 2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus = 4
    """ DRL learner """
    action_type = Learner.do_learn
    learner_type = Learner.deep_reinforcement_learner
    nb_epochs = 25000
    nb_shuffles = 50
    nb_sequences = 10
    training_data_every_epoch = False
    cap_target_at_network_count = True
    update_target_network_frequency = 500
    update_target_network_threshold = 1e-3
    max_nb_target_network_update = 40
    max_target_not_increasing_epochs_pct = 0.5
    max_target_uptick = 0.01
    learning_rate = 1e-3
    scheduler = DeepReinforcementLearner.exponential_scheduler
    gamma_scheduler = 0.9999
    """ ... and its network config """
    network_type = DeepLearning.fully_connected_net
    layers_description = (128, 64, 32)
    one_hot_encoding = True
    """ Kick-off the Deep Reinforcement Learner ... """
    learning_file_name = Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ ... and plot its learning data """
    action_type = Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black
As can be seen on the next page, which I obtained from running the above code snipet (keep in mind that every run is going to be slightly different due to the random puzzles being generated), the training stopped after about 17,100 epochs as the 40 target network updates had been reached. By that point, the DRL learner had seen 40\% of the possible puzzles, and the very last MSE loss (after update, so out-of-sample) was around 0.4, corresponding to 2\% of the max target cost. It is interesting to notice that since I have shuffled the sequences only 50 times, and since the (n=4, m=2) is quite constrained in terms of possible moves, the max target ever produced by the network was only around 25, whereas we know the the God number of this dimension is 36. It is therefore likely that the resulting network would not produce very optimal solutions for puzzles whose cost is in the region [25, 36].

>>>>

\afblue
\paragraph{}{\textbf{python code -- deep reinforcement learner}}
\begin{python}
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deepreinforcementlearner import DeepReinforcementLearner
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n = 4
    m = 2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus = 4
    """ DRL learner """
    action_type = Learner.do_learn
    learner_type = Learner.deep_reinforcement_learner
    nb_epochs = 25000
    nb_shuffles = 50
    nb_sequences = 10
    training_data_every_epoch = False
    cap_target_at_network_count = True
    update_target_network_frequency = 500
    update_target_network_threshold = 1e-3
    max_nb_target_network_update = 40
    max_target_not_increasing_epochs_pct = 0.5
    max_target_uptick = 0.01
    learning_rate = 1e-3
    scheduler = DeepReinforcementLearner.exponential_scheduler
    gamma_scheduler = 0.9999
    """ ... and its network config """
    network_type = DeepLearning.fully_connected_net
    layers_description = (128, 64, 32)
    one_hot_encoding = True
    """ Kick-off the Deep Reinforcement Learner ... """
    learning_file_name = Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ ... and plot its learning data """
    action_type = Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black
As can be seen on the next page, which I obtained from running the above code snipet (keep in mind that every run is going to be slightly different due to the random puzzles being generated), the training stopped after about 17,100 epochs as the 40 target network updates had been reached. By that point, the DRL learner had seen 40\% of the possible puzzles, and the very last MSE loss (after update, so out-of-sample) was around 0.4, corresponding to 2\% of the max target cost. It is interesting to notice that since I have shuffled the sequences only 50 times, and since the (n=4, m=2) SP is quite constrained in terms of possible moves, the max target ever produced by the network was only around 25, whereas we know the God number for this dimension is 36 (see later section \ref{sec:SPLowDimension}). It is therefore likely that the resulting network would not produce very optimal solutions for puzzles whose cost is in the region [25, 36].
